My title

### 2024-03-17 paper/paper.qmd
Edits

Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand. In practice `rstanarm` converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beta_2 \times \mbox{education}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 5.02) \\
\beta_2 &\sim \mbox{Normal}(0, 6.34)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `modelsummary` package of @modelsummary and `here` package of @here. We use the default priors from `rstanarm`.

@@

We expect a positive relationship between .... In particular...

>>>>

Define $y_i$ as the is the political preference of the respondent and equal to 1 if Biden and 0 if Trump. Then $\text{gender}_i$ is the gender of the respondent and $\text{education}_i$ is the highest education of the respondent.
$\beta_1$ and $\beta_2$ represent the coefficients associated with the predictor variables (gender and education level of respondent, respectively).
We could estimate the parameters using `stan_glm()`. Note that the model is a generally accepted short-hand. In practice `rstanarm` converts categorical variables into a series of indicator variables and there are multiple coefficients estimated. In the interest of run-time we will randomly sample 1,000 observations and fit the model on that, rather than the full dataset.

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beta_2 \times \mbox{education}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5)
\end{align}

In our model, these prior distributions are assumed to be normal distributions with mean 0 and standard deviation 2.5, where the prior distributions capture uncertainty about their values before observing the data.
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `modelsummary` package of @modelsummary and `here` package of @here. We use the default priors from `rstanarm`.

@@
